\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-21 WOOT/Files/introduction.tex
minor revision of intro

On the other side of the coin, the security of USB has caused serious problems.
The designers of USB protocol didn't care much about security issues as they wanted to make a trusted protocol.
There are more than four hundred vulnerabilities referencing USB on CVE list~\cite{website:CVE-list}.
As a result, lots of attackers make use of these vulnerabilities and the \textit{trust-by-default} characteristics of USB to conduct attacks, which puts the privacy and financial security of USB users in danger~\cite{sok}.

BadUSB is a well-known class of firmware attacks~\cite{badusb}.
These attacks are conducted through modification of the device firmware, which will disguise normal USB devices as other types of devices that are \textit{trust-by-default} by the hosts.
Typical simulated devices include human interface devices (short for HID, including keyboards, mice, etc.) and disks.
Utilizing BadUSB, attackers can pretend themselves as normal users, such as typing malicious code to victim computers, downloading and executing malicious scripts, and copying out private data from disks.
Such attacks can easily escape from traditional anti-virus software, since it is very hard to distinguish them with normal usage.

Despite the advantageous features of BadUSB, there exist several limitations as follows.
(1) Attackers can't conduct attacks precisely, which decreases the capabilities of BadUSB attacks.
While performing attacks on another host, the attackers can neither know the current user interface (UI) status nor obtain the consequences of their attacking actions to take subsequent moves.
For example, it is hard for attackers to locate specific functional UI patterns like buttons and links on victim computers by disguising USB devices as mice.
That explains why typical BadUSB attacks often only stay in command line, using commands to download malicious scripts for execution.
However, these attacks may be intercepted by anti-virus software or firewall due to the usage of network.
(2) To our best knowledge, existing BadUSB attacks only utilize the features of USB 2.0.
The releasing of USB 3.0 makes USB more powerful, with a higher transmission rate for data and the support towards a larger range of devices including DisplayPort, HDMI, PowerDelivery, etc.
BadUSB attacks can become more effective with the help of USB 3.0.
(3) There have emerged multiple efficacious countermeasures after the appearance of BadUSB.
For example, GoodUSB offers a defence method by limiting the functions of USB devices to users' expectations~\cite{tian2015defending}.
It provides a graphical interface for user to describe the functionalities or roles of the USB device and reject any usage beyond the description.
\shuqing{Can't bypass USBCheckIn.}

In this work, we proposed our approach to address the limitations mentioned above and implemented a multi-mode attack model of USB, named \tool.
\tool extends BadUSB to support the features of USB Type-C.
Since USB Type-C is capable to transfer video steaming data, \tool could obtain the information of victim's graphical interface during attacks.
Combining it with simulation of traditional HIDs like keyboards and mice, attackers can perform precise attacks.
We did experiments to verify that \tool could also bypass most of the countermeasures for BadUSB since they often rely on interaction with the graphical interface.
Moreover, we implemented multiple attacking modes of USB attacks based on our approach to verify its effectiveness, including scripting, remote control and privacy extraction.
To improve the efficiency and performance of \tool, we designed a filtering algorithm to preprocess the video data before network transmission.
After implementation, we conducted a series of experiments for each attack mode.
\shuqing{Case study, evaluation, notable results.}

>>>>

On the other side of the coin, the security of USB has caused serious problems.
The designers of USB protocol did not care much about security issues as they wanted to make a easy-to-use protocol.
There are more than four hundred vulnerabilities referencing USB on CVE list~\cite{website:CVE-list}.
As a result, many attackers exploit these vulnerabilities and the \textit{trust-by-default} characteristics of USB to conduct attacks, which puts the privacy and financial security of USB users in danger~\cite{sok}.

BadUSB is a well-known class of firmware attacks~\cite{badusb}.
These attacks are conducted through modification of the device firmware, which will disguise normal USB devices as other types of devices that are \textit{trust-by-default} by the hosts.
Typical simulated devices include HID (short for human interface devices, including keyboards, mice, etc.) and disks.
Utilizing BadUSB, attackers can pretend themselves as normal users, typing malicious code to victim computers, downloading and executing malicious scripts, and copying out private data from disks.
Such attacks can easily escape from traditional anti-virus software, since it is very hard to distinguish them from normal USB devices.

Despite the advantageous features of BadUSB, there exist several limitations as follows.
(1) Attackers can't conduct attacks precisely, which decreases the capabilities of BadUSB attacks.
When performing attacks on another host, the attackers can not obtain the current user interface (UI) status which limits them from taking subsequent moves.
For example, it is hard for attackers to locate specific functional UI patterns like buttons and links on victim computers by disguising USB devices as mice.
That explains why typical BadUSB attacks often only stay in command line, using commands to download malicious scripts for execution.
However, these attacks may be intercepted by anti-virus software or firewall due to the usage of host network.
(2) To our best knowledge, existing BadUSB attacks only utilize the features of USB 2.0.
The releasing of USB 3.0 makes USB more powerful, with a higher transmission rate for data and the support towards a larger range of peripherals including DisplayPort, HDMI, PowerDelivery, etc.
BadUSB attacks can become more effective with the help of USB 3.0.
(3) There have emerged multiple efficacious countermeasures after the appearance of BadUSB.
For example, GoodUSB offers a defence method by limiting the functions of USB devices to users' expectations~\cite{tian2015defending}.
It provides a graphical interface for user to describe the functionalities or roles of the USB device and reject any usage beyond the description.
\shuqing{Can't bypass USBCheckIn.}

In this work, we proposed our approach to address the limitations mentioned above and implemented a multi-mode attack model of USB, named \tool.
\tool extends BadUSB to support the features of USB Type-C.
Since USB Type-C is capable to transfer video stream data, \tool could obtain the information of victim's graphical interface during attacks.
Combining it with simulation of traditional HIDs like keyboards and mice, attackers can perform precise attacks.
We did experiments to verify that \tool could also bypass most of the countermeasures for BadUSB since they often rely on interaction with the graphical interface.
Moreover, we implemented multiple attacking modes of USB attacks based on our approach to verify its effectiveness, including scripting, remote control and privacy extraction.
To improve the efficiency and performance of \tool, we designed a filtering algorithm to preprocess the video data before network transmission.
After implementation, we conducted a series of experiments for each attack mode.
\shuqing{Case study, evaluation, notable results.}
